RJObject Paper

### 2014-06-08 Documents/Paper/ms.tex
paper

\title{Document Title}
\author{Brendon J. Brewer}

\begin{document}
\maketitle

\section{Introduction}

\section{Spatial Distribution}
Suppose the two uniform variables are $u_1$ and $u_2$.
These get turned into an elliptical thing 
(centered at zero, aligned along the $x$-axis)
by the following one-to-one transformation:
\begin{eqnarray}
x &=& \frac{\mathcal{R}(u_1)}{\sqrt{q}}\cos\left(2\pi u_2\right)\\
y &=& \mathcal{R}(u_1)\sqrt{q}\sin\left(2\pi u_2\right)
\end{eqnarray}
where $\mathcal{R}(u)$ is some function that determines the
radial profile. So far I am using an exponential distribution:
\begin{eqnarray}
\mathcal{R}(u) = -\mu\log(1 - u).
\end{eqnarray}
The probability density for $x$ and $y$ is given by:
\begin{eqnarray}
p(x, y)
&=& \frac{p(u_1, u_2)}{\left|\det \mathbf{J}\right|}
\end{eqnarray}
where $\mathbf{J}$ is the Jacobian of the transformation:
\begin{eqnarray}
\mathbf{J} &=&
\left(
\begin{array}{cc}
\frac{\partial x}{\partial u_1} & \frac{\partial x}{\partial u_2}\\
\frac{\partial y}{\partial u_1} & \frac{\partial y}{\partial u_2}
\end{array}
\right)
\end{eqnarray}
Let's calculate the terms. Here they are:
\begin{eqnarray}
J_{11} &=& \frac{\mathcal{R}'(u_1)}{\sqrt{q}}\cos\left(2\pi u_2\right)\\
J_{12} &=& -\frac{2\pi\mathcal{R}(u_1)}{\sqrt{q}}\sin\left(2\pi u_2\right)\\
J_{21} &=& \mathcal{R}'(u_1)\sqrt{q}\sin\left(2\pi u_2\right)\\
J_{22} &=&  2\pi\mathcal{R}(u_1)\sqrt{q}\cos\left(2\pi u_2\right)
\end{eqnarray}
The determinant is:
\begin{eqnarray}
\det \mathbf{J} &=& J_{11}J_{22} - J_{12}J_{21}\\
&=& 2\pi\mathcal{R}(u_1)\mathcal{R}'(u_1)\cos^2\left(2\pi u_2\right)
+2\pi\mathcal{R}(u_1)\mathcal{R}'(u_1)\sin^2\left(2\pi u_2\right)\\
&=& 2\pi\mathcal{R}(u_1)\mathcal{R}'(u_1)
\end{eqnarray}
With the exponential choice, this is:
\begin{eqnarray}
\det \mathbf{J} &=& -2\pi\mu\frac{\log(1 - u_1)}{1 - u_1}
\end{eqnarray}

>>>>

\title{RJObject Paper}
\author{Brendon J. Brewer}

\begin{document}
\maketitle
\abstract{This is the abstract.}

\section{Introduction}
Many inference problems have the following structure.

\section{Sinusoidal Example}
Phase transition

\section{``Transit'' Example}
